Token-level author diarization using clustering of stylistic contexts

### 2017-06-04 paper/paper.tex
no comment

As its feature transformation $f_\mathrm{t}$, Model A uses feature scaling to zero mean and unit variance for each document separately. Model B uses a trainable transformation which requires a fixed basic feature space. Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$. Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$. We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_\mathrm{b}'}\rightarrow\mathbb{R}^{n_\mathrm{t}}$ with trainable parameters $\vect{\theta}_T$, i.e. we want to maximize segregation and compactness of groups of transformed feature vectors grouped by their target author label. Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i'))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_\mathrm{t}}$. We define the following loss in order to optimize the transformation $T$:

@@

For Task \emph{b} we split the dataset in two halves as well. Grid search for the best hyperparameters was performed for agglomerative clustering. The best performance on the training set was obtained with euclidean affinity and average linkage. For Task \emph{c} we should have somehow determined the number of clusters. Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e. this is not a hyperparameter which should be known in advance. Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments. We tested DBSCAN and affinity propagation algorithms.

>>>>

As its feature transformation $f_\mathrm{t}$, Model A uses feature scaling to zero mean and unit variance for each document separately. Model B uses a trainable transformation which requires a basic feature space of fixed dimension. Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$. Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$. We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_\mathrm{b}'}\rightarrow\mathbb{R}^{n_\mathrm{t}}$ with trainable parameters $\vect{\theta}_T$, i.e. we want to maximize segregation and compactness of groups of transformed feature vectors grouped by their target author label. Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i'))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_\mathrm{t}}$. We define the following loss in order to optimize the transformation $T$:

@@

For Task \emph{b} we split the dataset in two halves as well. Grid search for the best hyperparameters was performed for agglomerative clustering. The best performance on the training set was obtained with Euclidean affinity and average linkage. For Task \emph{c} we should have somehow determined the number of clusters. Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e. this is not a hyperparameter which should be known in advance. Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments. We tested DBSCAN and affinity propagation algorithms.
